$Z_3$ topological order in the quantum dimer-pentamer model

### 2017-03-10 qdpm_paper.tex
Updated section II based on Ty's comments

We may understand the emergence of the $Z_2$ topologically ordered phase of IGTs from the QDM and QFPLM from the following picture. The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint  have U(1) charge $Q_v = \pm 2$ (see \tabref{tab:defects}). It is known that coupling a $U(1)$ gauge field to a dynamic charge $q$ matter field can result in a $Z_q$ gauge theory~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result. We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory (see \appref{sec:Z3GT} for a review of $Z_3$ gauge theory).

>>>>

We may understand the emergence of the $Z_2$ topologically ordered phase of IGTs from the QDM and QFPLM from the following picture. The additional vertex configurations that are allowed in the IGTs relative to the models with a dimer number constraint  have U(1) charge $Q_v = \pm 2$ (see \tabref{tab:defects}). It is known that when a $U(1)$ gauge field is coupled to a dynamic charge $q$ matter field, this results in a $Z_q$ gauge theory when the matter field condenses~\cite{Fradkin1979}; as in the IGT's we have added dynamic charge 2 defects to the underlying $U(1)$ symmetric model, and we may expect a $Z_2$ gauge theory to result. We note that pentamers are charge $\pm3$ objects in the QDM (see \tabref{tab:defects}); thus below we investigate whether introducing pentamers into the QDM leads to an effective $Z_3$ gauge theory (see \appref{sec:Z3GT} for a review of $Z_3$ gauge theory).
